---
title: "simpleRegress"
author: "Michelle Cervantes"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
pairs(bears)
```

It appears that HEADLEN may be a better variable  



```{r}
headlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(headlen)
summary.lm(headlen)
```

## Conclusion   

The model using HEADLEN is a better model than NECK. This is because the adjusted r-squared for the the HEADLEN model is 0.8434, the adjusted r-squared for the NECK model was 0.7476. The model with the larger r-squared value fits better. 